Nice people or potential cooperators when keeping promises

### 2019-08-09 behavioral-promises/behavioral-promises.Rmd
Using springer template

---
title: "Nice people or potential cooperators when keeping promises: an experimental and Bayesian account for two explanations"
author: "Said Jiménez"
date: "August 2019"
output:  
  pdf_document:
    number_sections: true
    keep_tex: true
fontsize: 12pt
bibliography: promises.bib
csl: apa.csl
---

@@

```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%', out.height='100%'}

@@

kable(tabla1, 
      digits = 3, 
      booktabs = T,
      col.names = c("Term", "Estimate", "Est.Error", "Lower", "Upper"),
      caption = c("Posterior coefficients estimates")) %>%
  add_header_above(c(" ", " " = 2, "95 % CI" = 2)) %>% 
  kable_styling(latex_options = "hold_position")

>>>>

---
title: Nice people or potential cooperators when keeping promises
subtitle: An experimental and Bayesian account for two explanations
titlerunning: Nice people or potential cooperators
authorrunning: S. Jiménez, et al.
geometry: margin=1in
thanks: 
authors: 
- name: Said Jiménez 
  address: Department of Psychology, National University of México (UNAM)
  email: said.ejp@gmail.com

- name: Kamila E. Sip 
  address: Institute for Neuroleadership
  email: kami.sip@gmail.com

- name: Roberto E. Mercadillo
  address: Department of Biology, Universidad Autónoma Metropolitana (UAM)
  email: emmanuele.mercadillo@gmail.com

- name: Diego Angeles-Valdez
  address: Institute of Neurobiology, UNAM
  email: anglsd_20@hotmail.com

- name: Jairo Muñoz-Delgado
  address: Investigaciones en Neurociencias, INPRF
  email: munozd460@gmail.com

- name: Juan J. Sánchez-Sosa
  address: Department of Psychology, National University of México (UNAM)
  email: jujosaso@gmail.com

- name: Eduardo A. Garza-Villarreal
  address: Institute of Neurobiology, UNAM
  email: egarza@gmail.com

keywords:
- Deception
- Hierarchical Bayesian Models
- Bayesian Cumulative Models
- Social closeness
- Promises

#PACS: 
#- PAC1
#- superPAC

#MSC:
#- MSC code 1
#- MSC code 2

abstract: |
  Promises increase cooperation between non-genetically related individuals, however, lies and betrayals occur daily in close social relationships. Despite this, the effect of social closeness on the decision to keep or break a promise has not been studied. We conducted an experiment in which subjects could freely decide if they broke or kept their promise to three partners with different levels of social closeness: null (computer), low (strange) and high (friend). If subjects keep their word with the computer, it provides evidence in favor of intrinsic motivation (comply to do the correct thing), otherwise extrinsic motivation would be supported (comply to facilitate future cooperation). Using Hierarchical Bayesian Modeling, we find that if social closeness increases, the probability of breaking promises decreases monotonically, the evidence ratio in favor to the hypothesis stranger < computer was 7.47, and friend < stranger was 8.64. Furthermore, using Bayesian Cumulative Modeling we find that subjects were very consistent between their promises and the subsequent decisions they make. Although is more probable that our subjects keep their promises to any of the three partners, there is a proportion of transgressions to the computer, whose inference excludes zero with a 95% posterior probability. Also, subjects never broke the promise to their friends. Our results indicate that subjects are predominantly "nice people" because they keep their promises even to partners without social closeness, however, if the subjects are not certain that their partner will also be a "potential cooperator", dishonesty emerges in the form of broken promises.

bibliography: bibliography.bib
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
output: rticles::springer_article
---

@@

```{r fig5, fig.cap='Posterior predictive over pay back rate', out.width='100%', out.height='42%'}

@@

knitr::kable(tabla1, 
      digits = 3, 
      booktabs = T,
      col.names = c("Term", "Estimate", "Est.Error", "Lower", "Upper"),
      caption = c("Posterior coefficients estimates")) %>%
  add_header_above(c(" ", " " = 2, "95 % CI" = 2)) %>% 
  kable_styling(position = "left")
